Summary

### 2016-02-04 inst/examples/summary.Rmd
ok
fixed bugs with bibliographica updates

---
title: "Summary"
author: "Niko Ilomäki and Leo Lahti"
date: "Tuesday, October 20, 2015"
output: markdown_document
---

@@

```{r missing2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
dfs <- df %>% select(author, publication_place, country, publication_year, published_from, published_till, corporate, area, pagecount, gatherings, width, height, paper.consumption.km2, publisher, self_published)
success <- as.data.frame(t(apply(dfs, 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
original.nonNA <- as.data.frame(t(apply(select(df.orig, publication_place, publication_time, corporate, physical_extent, physical_dimension, publisher, author_name), 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))

# Compare the number of non-NA entries in preprocessed data to number
# of non-NA entries in the original data:
real.success <- c()
real.success[["publication_place"]] <- success$publication_place/original.nonNA$publication_place
real.success[["country"]] <- success$country/original.nonNA$publication_place
real.success[["publication_year"]] <- success$publication_year/original.nonNA$publication_time
real.success[["published_from"]] <- success$published_from/original.nonNA$publication_time
real.success[["published_till"]] <- success$published_till/original.nonNA$publication_time
real.success[["corporate"]] <- success$corporate/original.nonNA$corporate
real.success[["publisher"]] <- success$publisher/original.nonNA$publisher
real.success[["self_published"]] <- success$self_published/original.nonNA$publisher
real.success[["pagecount"]] <- success$pagecount/original.nonNA$physical_extent
real.success[["area"]] <- success$area/original.nonNA$physical_dimension
real.success[["gatherings"]] <- success$gatherings/original.nonNA$physical_dimension
real.success[["author"]] <- success$author/original.nonNA$author
real.success[["paper"]] <- success$paper.consumption.km2/sum(rowMeans(!is.na(df.orig[, c("physical_extent", "physical_dimension")])) == 1)
par(mar = c(3, 8, 2, 1)); barplot(100*sort(real.success), horiz = T, main = "Real success rate (selected fields)", las = 1, xlim = c(0, 100), xlab = "Success rate (%)")
```

@@

>>>>

---
title: "Summary"
author: "Leo Lahti and Niko Ilomäki"
date: "Feb 3, 2016"
output: markdown_document
---

@@

```{r missing2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
dfs <- df %>% select(author, publication_place, country, publication_year, publication_year_from, publication_year_till, corporate, area, pagecount, gatherings, width, height, paper.consumption.km2, publisher, self_published)
success <- as.data.frame(t(apply(dfs, 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
original.nonNA <- as.data.frame(t(apply(select(df.orig, publication_place, publication_time, corporate, physical_extent, physical_dimension, publisher, author_name), 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))

# Compare the number of non-NA entries in preprocessed data to number
# of non-NA entries in the original data:
real.success <- c()
real.success[["publication_place"]] <- success$publication_place/original.nonNA$publication_place
real.success[["country"]] <- success$country/original.nonNA$publication_place
real.success[["publication_year"]] <- success$publication_year/original.nonNA$publication_time
real.success[["publication_year_from"]] <- success$published_from/original.nonNA$publication_time
real.success[["publication_year_till"]] <- success$published_till/original.nonNA$publication_time
real.success[["corporate"]] <- success$corporate/original.nonNA$corporate
real.success[["publisher"]] <- success$publisher/original.nonNA$publisher
real.success[["self_published"]] <- success$self_published/original.nonNA$publisher
real.success[["pagecount"]] <- success$pagecount/original.nonNA$physical_extent
real.success[["area"]] <- success$area/original.nonNA$physical_dimension
real.success[["gatherings"]] <- success$gatherings/original.nonNA$physical_dimension
real.success[["author"]] <- success$author/original.nonNA$author
real.success[["paper"]] <- success$paper.consumption.km2/sum(rowMeans(!is.na(df.orig[, c("physical_extent", "physical_dimension")])) == 1)
par(mar = c(3, 8, 2, 1)); barplot(100*sort(real.success), horiz = T, main = "Real success rate (selected fields)", las = 1, xlim = c(0, 100), xlab = "Success rate (%)")
```

@@

[Discarded author first names](output.tables/author_name_discarded_first.csv)

[Discarded author last names](output.tables/author_name_discarded_last.csv)

[Authors missing life years](output.tables/authors_missing_lifeyears.csv)
